Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-18 paper.tex
add a bit more cyclus discussion to intro

\newpage
\begin{abstract}
TODO: Write this abstract.
\end{abstract}

@@

@@

One of the major motivations for the development of the Cyclus fuel cycle
simulator \cite{cyclus_2015} was creating a simulation environment that is
more expressive than more traditional fuel cycle simulators.  Cyclus was
designed with a plugin-style architecture that allows different models for
facility types to be swapped in and out trivially.  As a Cyclus simulation
walks through each time step, facilities engage in a market-like dynamic
resource exchange (DRE).  They broadcast requests for material and suppliers
respond with bids. The DRE then creates a network flow problem that it
optimizes to resolve which transactions actually occur.  The plugin
architecture combined with the DRE creates a powerful and flexible environment
for the natural comparison of different modeling paradigms.

Cyclus' agent-based architecture in concert with its dynamic resource exchange
has the ability to model fleet-based facilities.  However, Cyclus was designed
to enable modeling facilities individually with discrete flows enabling the
investigation of interesting real-world effects such as competition, reactor
cycle staggering, and individual reactor outages.

>>>>

\newpage

\begin{abstract}
TODO: Write this abstract.
\end{abstract}

@@

TODO: add good intro/overview paragraph

@@

One of the major motivations for the development of the Cyclus fuel cycle
simulator \cite{cyclus_2015} was creating a simulation environment that is
more expressive than more traditional fuel cycle simulators.  Cyclus was
designed with a plugin-style architecture that allows different models for
facility types, known as \emph{archetypes} to be swapped in and out trivially.

As a Cyclus simulation walks through each time step, facilities engage in a
market-like dynamic resource exchange (DRE).  They broadcast requests for
material and suppliers respond with bids. The DRE then creates a network flow
problem that is optimized to resolve which transactions actually occur.  The
plugin architecture combined with the DRE creates a powerful and flexible
environment for the natural comparison of different modeling paradigms.
Cyclus' agent-based architecture in concert with its dynamic resource exchange
has the ability to model fleet-based facilities.  However, Cyclus was designed
to enable modeling facilities individually with discrete flows enabling the
investigation of interesting real-world effects such as competition, reactor
cycle staggering, and individual reactor outages.

Cyclus was designed to operate natively in unix/linux type environments with
flexible ascriptable usage and input file format.  Cyclus holds its diverse
generated data into a powerful open-source database format.  In addition to
information about material flows and facility deployments, Cyclus' single-file
database contains version information about the archetypes used in a
simulation, the simulation input file, version of Cyclus used to run the
simulation, and the installed versions of Cyclus dependencies. This and other
features of Cyclus lend themselves well to automation, research provenance and
reproducibility, and large-scale computing.
